How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-17 docs/PhysicsPaper/StokesErosion.tex
NM

%---------------------------------------------------%
% From JFM 2020
\newcommand{\bd}{{\partial}}
\newcommand{\bigO}{{\mathcal{O}}}
\newcommand{\cc}{{\mathbf{c}}}
\newcommand{\CC}{{\mathbb{C}}}
\newcommand{\DD}{{\mathcal{D}}}
\newcommand{\DDD}{{\boldsymbol{\mathcal D}}}
\newcommand{\eeta}{{\boldsymbol\eta}}
\newcommand{\ff}{{\mathbf{f}}}
\newcommand{\grad}{{\nabla}}
\newcommand{\II}{{\mathbf{I}}}
\newcommand{\iin}{\mathrm{in}}
\newcommand{\llambda}{{\boldsymbol\lambda}}
\newcommand{\nn}{{\mathbf{n}}}
\newcommand{\NN}{{\mathcal{N}}}
\newcommand{\out}{\mathrm{out}}
\newcommand{\rr}{{\mathbf{r}}}
\renewcommand{\Re}{{\operatorname{Re}}}
\renewcommand{\Im}{{\operatorname{Im}}}
\newcommand{\RR}{{\mathbb{R}}}
\renewcommand{\ss}{{\mathbf{s}}}
\newcommand{\tar}{\mathrm{tar}}
\newcommand{\bary}{\mathrm{bary}}
\newcommand{\trap}{\mathrm{trap}}
\newcommand{\uu}{{\mathbf{u}}}
\newcommand{\UU}{{\mathbf{U}}}
\newcommand{\vv}{{\mathbf{v}}}
\newcommand{\xx}{{\mathbf{x}}}
\newcommand{\xxi}{{\boldsymbol{\xi}}}
\newcommand{\yy}{{\mathbf{y}}}
\newcommand{\mcaption}[2]{\caption{\small \em #1}\label{#2}} 
\newcommand{\secref}[1]{\ref{#1}}
\def\gap{\hspace*{.2in}}
% Nick's below
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\ppd}[2]{\frac{\partial^2 #1}{{\partial #2}^2}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\Vn}{V_\nn}
\newcommand{\Vs}{V_\ss}
\newcommand{\CE}{C_E}
%---------------------------------------------------%

@@

@@

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig2}
\includegraphics[width = 0.99 \textwidth]{./figs/fig2.pdf}
\caption{A single simulation of porous-medium erosion. The initial configuration consists of XX circular bodies of random size and position, as seen in Fig.~1? a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases. b) Resistance to flow can be characterized by either the inverse permeability, $1/k$, or the cumulative drag, the two of which are related through \eqref{ResistDrag}. Both are seen to decrease as the medium erodes, and relationship \eqref{ResistDrag} is confirmed by the simulation data.
c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium. Both quantities increase with time as the medium erodes, but at different rates due to changes in the microstructure and channelization of the medium.
}
\end{figure*}
%---------------------------------------------------------%

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig3}
\includegraphics[width = 0.99 \textwidth]{./figs/fig3.pdf}
\caption{
Permeability
}
\end{figure*}
%---------------------------------------------------------%

@@

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig4}
\includegraphics[width = 0.99 \textwidth]{./figs/fig4.pdf}
\caption{
Tortuosity
}
\end{figure*}
%---------------------------------------------------------%

>>>>

%---------------------------------------------------%
% From JFM 2020
\newcommand{\bd}{{\partial}}
\newcommand{\bigO}{{\mathcal{O}}}
\newcommand{\cc}{{\mathbf{c}}}
\newcommand{\CC}{{\mathbb{C}}}
\newcommand{\DD}{{\mathcal{D}}}
\newcommand{\DDD}{{\boldsymbol{\mathcal D}}}
\newcommand{\eeta}{{\boldsymbol\eta}}
\newcommand{\ff}{{\mathbf{f}}}
\newcommand{\grad}{{\nabla}}
\newcommand{\II}{{\mathbf{I}}}
\newcommand{\iin}{\mathrm{in}}
\newcommand{\llambda}{{\boldsymbol\lambda}}
\newcommand{\nn}{{\mathbf{n}}}
\newcommand{\NN}{{\mathcal{N}}}
\newcommand{\out}{\mathrm{out}}
\newcommand{\rr}{{\mathbf{r}}}
\renewcommand{\Re}{{\operatorname{Re}}}
\renewcommand{\Im}{{\operatorname{Im}}}
\newcommand{\RR}{{\mathbb{R}}}
\renewcommand{\ss}{{\mathbf{s}}}
\newcommand{\tar}{\mathrm{tar}}
\newcommand{\bary}{\mathrm{bary}}
\newcommand{\trap}{\mathrm{trap}}
\newcommand{\uu}{{\mathbf{u}}}
\newcommand{\UU}{{\mathbf{U}}}
\newcommand{\vv}{{\mathbf{v}}}
\newcommand{\xx}{{\mathbf{x}}}
\newcommand{\xxi}{{\boldsymbol{\xi}}}
\newcommand{\yy}{{\mathbf{y}}}
\newcommand{\mcaption}[2]{\caption{\small \em #1}\label{#2}} 
\newcommand{\secref}[1]{\ref{#1}}
\def\gap{\hspace*{.2in}}
% Nick's below
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\ppd}[2]{\frac{\partial^2 #1}{{\partial #2}^2}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\Vn}{V_\nn}
\newcommand{\Vs}{V_\ss}
\newcommand{\CE}{C_E}
\newcommand{\thL}{$\theta$--$L$}
%---------------------------------------------------%

@@

%-----------------------------------------------------------------------------------------------%
\subsection{Interface evolution}
%-----------------------------------------------------------------------------------------------%

% COPIED STRAIGHT FROM JFM 2020
\nick{PLAGERIZED}
We use the time stepping method outlined in our previous
work~\citep[see][section 3.3]{qua-moo2018} which we briefly summarize
here.  The erosion rate loses differentiability if the shear stress
changes sign, and this leads to corners developing on $\gamma$ and
numerical instabilities.  Therefore, we modify the erosion rate, $V_\nn$
in equation~\eqref{eqn:erosionModel}, with
\begin{align}
  \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(
    \frac{L}{2\pi} \kappa - 1 \right),
\end{align}
where $\epsilon \ll 1,$ $\langle \cdot \rangle$ is the spatial average,
$L$ is the length of $\gamma$, and $\kappa$ is the curvature of
$\gamma$.  The new erosion model penalizes regions of high curvature,
but does not change the total length of each body.  Moreover, to
increase the overall stability of the method, a narrow Gaussian filter
is applied to the erosion rate at each time step.

Rather than tracking the $(x,y)$ coordinates, the {\thL} coordinates are
tracked. In addition, tangential velocity fields are used to maintain
an equispaced discretization. Time stepping is performed with a
second-order Implicit-Explicit Runge-Kutta method. In particular, the
diffusive term corresponding to the curvature penalization term is
discretized implicitly, and all other terms, which are non-stiff, are
treated explicitly.  By using this time stepping method in conjunction
with the Barycentric rule, we stably evolve the eroding bodies.

@@

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig2}
\includegraphics[width = 0.99 \textwidth]{./figs/fig2.pdf}
\caption{A single simulation of porous-medium erosion. The initial configuration consists of 80 circular bodies of random size and position, as seen in Fig.~\ref{fig1}. a) As the medium erodes, the fraction of solid-body area decreases, or, equivalently, the porosity increases. b) Resistance to flow can be characterized by either the inverse permeability, $1/k$, or the cumulative drag, the two of which are related through \eqref{ResistDrag}. Both are seen to decrease as the medium erodes, and relationship \eqref{ResistDrag} is confirmed by the simulation data.
c) The relationship between permeability $k$ and porosity $\phi$ for the eroding medium. Both quantities increase with time as the medium erodes, but at different rates due to changes in the microstructure and channelization of the medium.
}
\end{figure*}
%---------------------------------------------------------%
% Data from 80-4

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig3}
\includegraphics[width = 0.99 \textwidth]{./figs/fig3.pdf}
\caption{
Permeability
}
\end{figure*}
%---------------------------------------------------------%
% Data from 80-4

@@

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering \label{fig4}
\includegraphics[width = 0.99 \textwidth]{./figs/fig4.pdf}
\caption{
Tortuosity
}
\end{figure*}
%---------------------------------------------------------%
% Data from 80-4
